### 2021-04-28 architecture.tex
Avoid an overfull line in non-compressed version
at minimization of precedence cost.

It is easy to see that all precedences that sort the symbol costs in a non-increasing order
have the same precedence cost.
Since $\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}

>>>>

It is easy to see that all precedences that sort the symbol costs in a non-increasing order
have the same precedence cost.
Since
\iftoggle{COMPRESS}{$\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$}{$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$},
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}
